Precise Asymptotics of Transferring from Different Regression in High Dimensions

### 2021-06-12 revision_journal/exp.tex
revision wip
restructure exp

\section{Algorithmic implications}

@@

One estimator that is sometimes employed in the literature is simply an average of the OLS estimators for two tasks \cite{bastani2020predicting}
\be\label{eq_est_ave}\hat \beta^{\AV}(\lambda)=\lambda \cdot \hat \beta_1^{\STL}+ (1-\lambda)\cdot \hat \beta_2^{\STL},\ee
where $\lambda\in [0,1]$ is an averaging parameter subject to choice in practice, and we recall that the OLS estimators are given by
$$\hat \beta_i^{\STL}= [(X^{(i)})^\top X^{(i)}]^{-1}(X^{(i)})^\top Y^{(i)},\quad i=1,2.$$
The estimator in \eqref{eq_est_ave} is conventionally called an \emph{averaging estimator}.
In particular, when $\lambda=0$ and $1$, we get the OLS estimators for tasks 2 and 1, respectively.

@@

\paragraph{Further Studies on Text Classification Tasks}%\label{sec_text}

@@

%We fill in the details of the experimental procedure used for the results in Figure \ref{fig_ablation}.
%\squishlist
%	\item Task similarity: We select a similar and a dissimilar source task compared to the target task using domain knowledge.
%First pair: the customer review dataset (CR) , which predicts whether a review is positive or negative, is more similar to SST (sentiment treebank) than MPQA (question type).
%Second pair: SST is more similar to MR since they both concern about positive or negative opinions expressed the text.
%TREC is less similar to MR because the task is about question types.
%Third pair: MPQA (opinion polarity) is more similar to TREC (question type)
We evaluate the progressive training procedure on the six text classification datasets.
First, we conduct multi-task training over all $15$ two-task pairs from the six datasets.
We focus on task two's test accuracy and set $\tau$ as task two's test accuracy obtained via the standard round-robin training schedule.
We include all of task two's data and progressively add task one's data using the procedure described above.
Since the prediction accuracy has been controlled the same, we compare the computational cost.
We find that when averaged over all $15$ two-task pairs, this procedure requires only $45\%$ of the computational cost to reach the desired accuracy $\tau$ for task two.
%Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{progressively} during training.
%\textbf{Improving transfer learning training efficiency.}
%We show that Algorithm \ref{alg_inc_train} also applies to transfer learning settings.
%Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
Second, we conduct multi-task training on all six datasets jointly.
We extend our procedure to all six datasets. We include the data from all tasks except SST. For SST, we progressively add data similar to the above procedure.
We set $\tau$ to be the average test accuracy of all six tasks obtained using standard round-robin training.
We find that adding samples progressively from SST requires less than $35\%$ of the computational cost to reach the same average test accuracy $\tau$.
%As a further validation, excluding TREC, we observe similar comparative results.
%The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
%We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
%If TREC is not included, we see that only $25\%$ of the labeled data is needed.

>>>>

\section{Theoretical Implications}

@@

\subsection{Covariance Alignment}

%One estimator that is sometimes employed in the literature is simply an average of the OLS estimators for two tasks \cite{bastani2020predicting}
%\be\label{eq_est_ave}\hat \beta^{\AV}(\lambda)=\lambda \cdot \hat \beta_1^{\STL}+ (1-\lambda)\cdot \hat \beta_2^{\STL},\ee
%where $\lambda\in [0,1]$ is an averaging parameter subject to choice in practice, and we recall that the OLS estimators are given by
%$$\hat \beta_i^{\STL}= [(X^{(i)})^\top X^{(i)}]^{-1}(X^{(i)})^\top Y^{(i)},\quad i=1,2.$$
%The estimator in \eqref{eq_est_ave} is conventionally called an \emph{averaging estimator}.
%In particular, when $\lambda=0$ and $1$, we get the OLS estimators for tasks 2 and 1, respectively.

@@

\subsection{Progressive Training}%\label{sec_text}

@@

%We fill in the details of the experimental procedure used for the results in Figure \ref{fig_ablation}.
%\squishlist
%	\item Task similarity: We select a similar and a dissimilar source task compared to the target task using domain knowledge.
%First pair: the customer review dataset (CR) , which predicts whether a review is positive or negative, is more similar to SST (sentiment treebank) than MPQA (question type).
%Second pair: SST is more similar to MR since they both concern about positive or negative opinions expressed the text.
%TREC is less similar to MR because the task is about question types.
%Third pair: MPQA (opinion polarity) is more similar to TREC (question type)
We evaluate the progressive training procedure on the six text classification datasets.
First, we conduct multi-task training over all $15$ two-task pairs from the six datasets.
We focus on task two's test accuracy and set $\tau$ as task two's test accuracy obtained via the standard round-robin training schedule.
We include all of task two's data and progressively add task one's data using the procedure described above.
Since the prediction accuracy has been controlled the same, we compare the computational cost.
We find that when averaged over all $15$ two-task pairs, this procedure requires only $45\%$ of the computational cost to reach the desired accuracy $\tau$ for task two.
%Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{progressively} during training.
%\textbf{Improving transfer learning training efficiency.}
%We show that Algorithm \ref{alg_inc_train} also applies to transfer learning settings.
%Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
Second, we conduct multi-task training on all six datasets jointly.
We extend our procedure to all six datasets. We include the data from all tasks except SST. For SST, we progressively add data similar to the above procedure.
We set $\tau$ to be the average test accuracy of all six tasks obtained using standard round-robin training.
We find that adding samples progressively from SST requires less than $35\%$ of the computational cost to reach the same average test accuracy $\tau$.

\subsection{Rank Selection}
%As a further validation, excluding TREC, we observe similar comparative results.
%The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
%We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
%If TREC is not included, we see that only $25\%$ of the labeled data is needed.
